Untitled

### 2018-07-18 PaperCode.Rmd
New branch for quantiles
I realised calculating based on quantiles not price classes would be much easier. this requires much bigger changes

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 10, type, PropertyTypes)%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

@@

#Analyse Bootstrap

@@

@@

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()

@@

set.seed(4622)
Modeldf <- ModelMe  %>%
  vfold_cv(., V = 10, repeats = 100) %>%
  mutate(LogisticFOI = splits %>%
  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  LogisticOpen = splits %>%
  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  ForestOpen = splits %>% 
    map(., ~{rpart(OpenFormula, data=analysis(.x))})
  ) %>%
  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"), 
         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))

@@

ModComp <- Modeldf %>%
  select(LogFoiAcc, LogOpenAcc) %>%
  gather

@@

#The 95 percent confidence interval of the mean
QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))
#diff is 3.6M
QuantInfo[3]-QuantInfo[1]

>>>>

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes)%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

@@

#Make class plots of bootstrap results

@@

This chunk calculates for both A and B

@@

@@

set.seed(4622)
Modeldf <- ModelMe  %>%
  vfold_cv(., V = 10, repeats = 10) %>%
  mutate(LogisticFOI = splits %>%
  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  LogisticOpen = splits %>%
  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  ForestOpen = splits %>% 
    map(., ~{rpart(OpenFormula, data=analysis(.x))})
  ) %>%
  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"), 
         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))

@@

ModComp <- Modeldf %>%
  select(LogFoiAcc, LogOpenAcc, ForestOpenAcc) %>%
  gather

@@

#The 95 percent confidence interval of the mean
QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
QuantInfo
quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))
#diff is 3.6M
QuantInfo[3]-QuantInfo[1]
